---
title: "[Why R? 2018](http://whyr2018.pl/) workshops"
output: 
  html_document: 
    toc: yes
    css: toc.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

During the first day of Why R? 2018 conference, 2nd July 2018,  we are more than pleased to proposed following set of workshops.
Below you can find the plan and descriptions. See you at the venue!

_Please note that RLadies workshop is a free accompanying event that will take place in a separate building. We invite all participants that start their journey with R!_

> The plan of workshops (rooms and hours) is available here - https://whyr2018.github.io/plan/workshop_plans/)

# Why R? 2018 workshops

```{r, child = 'descriptions/04_Maps.Rmd'}

```

```{r, child = 'descriptions/08_xaringan.Rmd'}

```


```{r, child = 'descriptions/06_shiny_basics.Rmd'}

```


```{r, child = 'descriptions/03_DALEX.Rmd'}

```


```{r, child = 'descriptions/01_constructing_scales_from_survey_questions.Rmd'}

```

```{r, child = 'descriptions/02_From_RS_data_to_knowledge_-_Remote_Sensing_in_R.Rmd'}

```

```{r, child = 'descriptions/07_advanced_shiny.Rmd'}

```

```{r, child = 'descriptions/05_Keras.Rmd'}

```

