---
title: "[Why R? 2018](http://whyr2018.pl/) workshops"
subtitle: "The preference registration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

During the first day of Why R? 2018 conference, 2nd July 2018,  we are more than pleased to proposed following set of workshops.
Below you can find the plan and descriptions. To optimally schedule all workshops, we will send the workshop preference form to all registered participants.

See you at the venue!

_Please note that RLadies workshop is a free accompanying event that will take place in a separate building. We invite all participants that start their journey with R!_

# Proposed workshops

```{r, child = 'descriptions/04_Responding_to_analysis_and_communication_data_science_the_r_way.Rmd'}

```

```{r, child = 'descriptions/08_xaringan.Rmd'}

```


```{r, child = 'descriptions/06_shiny_basics.Rmd'}

```


```{r, child = 'descriptions/03_DALEX.Rmd'}

```


```{r, child = 'descriptions/01_constructing_scales_from_survey_questions.Rmd'}

```

```{r, child = 'descriptions/02_From_RS_data_to_knowledge_-_Remote_Sensing_in_R.Rmd'}

```

```{r, child = 'descriptions/07_advanced_shiny.Rmd'}

```

```{r, child = 'descriptions/05_Keras.Rmd'}

```

